opXRD: Open Experimental Powder X-ray Diffraction Database

### 2024-11-28 chapters/01_introduction.tex
Added paragraph arguing for publication via opXRD in interest of open science

% How to contribute? This aspect deserves a separate paragraph
The opXRD database is planned as a growing, community-driven initiative. The dataset we present here is the first version, but we hope to further increase the dataset size through active engagement with the pXRD community. Our primary objective is to minimize the effort and thus the barrier to contributing experimental data to the opXRD database. Thus, we developed a program that helps to find and share data from e.g. pXRD lab computers. In detail, users can select their most common pXRD file types, the program lists all files of that type, and users can select or deselect certain folders or files for sharing. Selected contributions will be uploaded to opXRD, processed to a common file format, and - if wanted - published on Zenodo on behalf of the contributors, before becoming part of the opXRD database. If labels are available, they can be shared with opXRD as well. Further details can be found on the opXRD website (Figure~\ref{fig:overview}).

@@

% TODOS: These papers talk about the importance of sharing raw diffraction data/ raw powder diffraction data them
%  1 | \cite{Aranda2018}
% 2 | Raw diffraction data and reproducibility

>>>>

% How to contribute? This aspect deserves a separate paragraph
The opXRD database is planned as a growing, community-driven initiative. The dataset we present here is the first version, but we hope to further increase the dataset size through active engagement with the pXRD community. Our primary objective is to minimize the effort and thus the barrier to contributing experimental data to the opXRD database. Thus, we developed a program that helps to find and share data from e.g. pXRD lab computers. In detail, users can select their most common pXRD file types, the program lists all files of that type, and users can select or deselect certain folders or files for sharing. Selected contributions will be uploaded to opXRD, processed to a common file format, and - if wanted - published on Zenodo on behalf of the contributors, before becoming part of the opXRD database. If labels are available, they can be shared with opXRD as well. Further details can be found on the opXRD website (Figure~\ref{fig:overview}). \\

As argued by Aranda and Kroon-Batenburg \textit{et al}.\cite{Aranda2018, Kroon-Batenburg2024}, sharing raw powder diffraction data is not only in the interest of furthering machine learning research but is also in line with open science principles. It furthers the ability of other researchers to reproduce published work and in turn, adds to the credibility of the publisher of the data. Considering our streamlined submission and post-processing framework, a publication of powder diffraction data through the opXRD database is a simple way of realizing these principles. Compared to uploading the data to Zenodo it also has the added benefit that the data is contributed towards a large, homogenous dataset with a standardized interface. This makes the data more easily accessible to other researchers and provides more value to researchers seeking great quantities of data compared to an isolated submission on Zenodo. \\

@@
